### 2021-01-06 slides_long/npu.tex

\begin{tikzpicture}[
        point/.style={coordinate},>=stealth',thick,draw=black!90,
        tip/.style={->,shorten >=0.007pt},every join/.style={rounded corners},
        fat/.style={-, ultra thick, opacity=0.5},every join/.style={rounded corners},
        path/.style={to path={-- (\tikztotarget)}},
        hv path/.style={to path={-| (\tikztotarget)}},
        vh path/.style={to path={|- (\tikztotarget)}},
        text height=1.5ex,text depth=.25ex]

  \matrix[column sep=3mm, row sep=3mm] {
    & \node (abs) [function] {$\mathrm{abs}$}; &
    \node (r) [vector] {$\bm r$}; & &
    \node (mult) [function] {$\mathrm{mult}$}; \\

    \node (x) [vector] {$\bm x$}; & & & &
    \node (wr) [trainable] {$\bm W_r$}; & \node (wi) [trainable] {$\bm W_i$}; &
    \node (odot) [function] {$\odot$}; &
    \node (y) [vector] {$\bm y$};\\

    & \node (bin) [function] {$\mathrm{bin}$}; &
    \node (k) [vector] {$\bm k$}; & &
    \node (sign) [function] {$\mathrm{sign}$}; \\
  };

  { [start chain]
    \chainin (x);
    \chainin (abs) [join=by {tip, vh path}];
    \chainin (r) [join=by path];
    \chainin (mult) [join=by tip];
    \chainin (odot) [join=by {hv path, tip}];
    \chainin (y) [join=by tip];
  }
  { [start chain]
    \chainin (x);
    \chainin (bin) [join=by {tip, vh path}];
    \chainin (k) [join=by path];
    \chainin (sign) [join=by tip];
    \chainin (odot) [join=by {tip, hv path}];
  }
  { [start chain] \chainin (wr); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (wr); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (wi); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (wi); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (r); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (k); \chainin (mult) [join=by tip]; }

>>>>

\begin{tikzpicture}[
        point/.style={coordinate},>=stealth',thick,draw=black!90,
        tip/.style={->,shorten >=0.007pt},every join/.style={rounded corners},
        fat/.style={-, ultra thick, opacity=0.5},every join/.style={rounded corners},
        hv path/.style={to path={-| (\tikztotarget)}},
        vh path/.style={to path={|- (\tikztotarget)}},
        text height=1.5ex,text depth=.25ex]

  \matrix[column sep=3mm, row sep=3mm] {
    & &
    \node (r) [vector] {$\bm r$}; & &
    \node (mult) [function] {$\mathrm{mult}$}; \\

    \node (x) [vector] {$\bm x$}; &
    \node (gate) [function] {$\mathrm{gate}$}; &
    \node (g) [trainable] {$\bm g$}; & &
    \node (wr) [trainable] {$\bm W_r$}; & \node (wi) [trainable] {$\bm W_i$}; &
    \node (odot) [function] {$\odot$}; &
    \node (y) [vector] {$\bm y$};\\

    & &
    \node (k) [vector] {$\bm k$}; & &
    \node (sign) [function] {$\mathrm{sign}$}; \\
  };

  { [start chain]
    \chainin (x);
    \chainin (gate) [join=by tip];
    \chainin (r) [join=by {vh path}];
    \chainin (mult) [join=by tip];
    \chainin (odot) [join=by {hv path, tip}];
    \chainin (y) [join=by tip];
  }
  { [start chain]
    \chainin (gate);
    \chainin (k) [join=by {vh path}];
    \chainin (sign) [join=by tip];
    \chainin (odot) [join=by {tip, hv path}];
  }
  { [start chain] \chainin (wr); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (wr); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (wi); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (wi); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (r); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (k); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (g); \chainin (gate) [join=by tip]; }
